This study addresses the regulation of ball position on a 3-degree-of-freedom (3-DOF) Stewart platform using a Proportional Integral Derivative (PID) control system. Previous research has primarily focused on either 2-DOF or 6-DOF platforms, leaving a significant knowledge gap concerning the application of control techniques to 3-DOF Stewart platforms. This research aims to bridge this gap by investigating the feasibility of PID control for regulating ball position on the platform.

To achieve this, an Arduino-based system incorporating three servos is employed for platform control, with the PID control system implemented in MATLAB Simulink. The ball's position is acquired through a webcam and computer vision, and the data are transmitted serially for processing.

While the results in terms of ball position regulation were unsatisfactory within the scope of this preliminary study due to time constraints and model play, the detection system demonstrated exceptional performance, and the Arduino-based servo control proved highly effective.

As a next step, further research will focus on enhancing the accuracy and robustness of the platform by implementing advanced control techniques such as Linear Quadratic Regulator (LQR), Fuzzy Logic, or Sliding Mode controllers. These methods are expected to address the limitations encountered in this study and improve the regulation of the ball's position on the 3-DOF Stewart platform.

In conclusion, this study presents a preliminary investigation into the regulation of ball position on a 3-DOF Stewart platform using PID control. Although the results were limited by time constraints and model play, the findings indicate the potential for achieving accurate ball position detection. Future research efforts will explore advanced control techniques to overcome the limitations encountered and enhance the platform's regulation capabilities.